---
title: "Final Group Project: AirBnB analytics"
date: "18 Oct 2021"
author: "Authors: Karim El Asmar, Stepan Emelianenko, Nelly Gray, Ziqi Li, Ray Park, Shirley Wan, Ditlev Meulengracht"
output:
  html_document:
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
---


```{r setup, include=FALSE}
# leave this chunk alone
options(knitr.table.format = "html") 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
  comment = NA, dpi = 300)
```


```{r load-libraries, include=FALSE}

library(tidyverse) # the usual stuff: dplyr, readr, and other goodies
library(lubridate) # to handle dates
library(GGally) # for correlation-scatter plot matrix
library(ggfortify) # to produce residual diagnostic plots
library(rsample) # to split dataframe in training- & testing sets
library(janitor) # clean_names()
library(broom) # use broom:augment() to get tidy table with regression output, residuals, etc
library(huxtable) # to get summary table of all models produced
library(kableExtra) # for formatting tables
library(moderndive) # for getting regression tables
library(skimr) # for skim
library(mosaic)
library(leaflet) # for interactive HTML maps
library(tidytext)
library(viridis)
library(vroom)
library(car)
```

# Introduction

In our final group assignment we are going to analyse data about Airbnb listings and fit a model to predict the total cost for two people staying 4 nights in an AirBnB in a city. We have chosen Amsterdam for our analysis. 

Our AirBnB data come from [insideairbnb.com](http://insideairbnb.com/get-the-data.html){target="_blank"}; it was originally scraped from airbnb.com. 

Below we load the data from Airbnb:

```{r load_data, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

#Load the data

listings <- vroom("http://data.insideairbnb.com/the-netherlands/north-holland/amsterdam/2021-09-07/data/listings.csv.gz") %>% 
       clean_names()

```


# Exploratory Data Analysis (EDA)


Let's first get an overview of our data. 

Afterward we will wrangle the data so that we can work with it in our models and plot some of the key relationships. 

## Data overview

We use `glimpse` and `skim` to gain a general view of the data. We have 74 variables and 16,116 observations. Variables include 24 character variables, 5 date variables, 8 logical variables, and 37 numeric variables. We also have some missing values throughout multiple of the variables in our data. 

```{r}
#Overview of Data
glimpse(listings)
skim(listings)

```


First out of interest we would like to plot a map of the raw dataset. 

By plotting a cluster map that shows the number of flat listed for rent, we want to visualise the concentration of listings in the area of Amsterdam

```{r}
#Map the concentration of listing in Amsterdam
listings %>% 
  leaflet() %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers(lng = ~longitude, 
                   lat = ~latitude, 
                   radius = 1,
                   fillOpacity = 0.3, 
                   popup = ~listing_url,
                   label = ~property_type,
                   clusterOptions = markerClusterOptions()
                   )
```

From this map, we concluded that more properties are available in the central area of Amsterdam. We would like to further investigate the relationship between the price of listings and the locations of properties.

We select some variables for our analysis which we believe would be relevant to determine the impact on prices.


We will hypothesize that the following are key variables which will will be using later on 

- `price`: cost per night (variable we will be use to predict)
- `property_type`: type of accommodation (House, Apartment, etc.)
- `room_type`:

  - Entire home/apt (guests have entire place to themselves)
  - Private room (Guests have private room to sleep, all other rooms shared)
  - Shared room (Guests sleep in room shared with others)

- `number_of_reviews`: Total number of reviews for the listing
- `review_scores_rating`: Average review score (0 - 100)
- `neighbourhood*`: three variables on a few major neighbourhoods in each city 
- `accomodations`: How many people can stay in the room per night
- `beds`: Number of beds
- `host_is_superhost`: Whether the host has superhost status
- `minimum_nights`: Minimum nights to stay in the Airbnb
- `bedrooms`: Number of bedrooms
- `reviews_per_month`: Number of reviews per month
- `availability_30`: Available stays next 30 days
- `license`: license number
- `instant_bookable`: Whether the room can be instantly booked

If you are interest in further information is is available [here](https://docs.google.com/spreadsheets/d/1iWCNJcSutYqpULSQHlNyGInUvHg2BoUGoNRIGa6Szc4/edit#gid=982310896)

Let's first filter for our variables of interest

```{r}

#Select the variables for further exploration

listings2 <- listings %>% 
  
  select(c("host_since", 
           "host_is_superhost", 
           "neighbourhood_cleansed", 
           "property_type", 
           "room_type", 
           "accommodates",
           "price",
           "review_scores_rating", 
           "number_of_reviews",
           "minimum_nights", 
           "reviews_per_month",
           "bedrooms","beds",
           "availability_30",
           "last_review",
           "license",
           "instant_bookable"))

# We want to choose the "bathrooms" as well, however,this variable has no values

```

## Data wrangling

Now let's ensure we can work with our data. 

First lets briefly look at our new dataset

```{r}
skim(listings2)
```


We see some issues that we will try and resolve. 


### Price

First:

Price is sometimes given as a character string and we would like it to be a double variable. 

Below we change the price to a double, i.e. a numeric variable. 

```{r}
#Change the 'price' to numeric
listings2 <- listings2 %>% 
  mutate(price = parse_number(price))

#Use `typeof(listing2$price)` to confirm that `price` is now stored as a number.
typeof(listings2$price)

```


### Licenses 

We then want to impute the missing value of "license" with logical judgement instead of a license number.

This will make our analysis simply focus on whether people have a license or not. 

```{r}
#Impute the missing value of “license”
listings2<-listings2 %>% 
  
  #Add yes or no depending on whether variable is missing
  mutate(license = ifelse(is.na(license), "no","yes"))


#Let's check our data by filtering for our license
License_check <- listings2 %>% 
  select(license)


#Let's take a glimpse at the results.
glimpse(License_check)

```

The code works as hoped. 


### Property types

Next, we look at the variable `property_type`. We use the `count` function to determine how many categories there are and their frequency.

This will be useful later to summarize our property types in larger categories as there will be more observations and less variables in the regression. 


```{r}
#Determine how many categories there are and their frequency
count_prop <- listings2 %>% 
  
  #Select variable of interest - i.e. property types
  select(property_type) %>% 
  
  #Count Number of each property type
  count(property_type) %>% 
  
  #Arrange by most frequent category
  arrange(desc(n)) %>% 
  
  #Create a new column for proportions
  mutate(percentage=n/sum(n)*100) #Determine the proportion of the total listings the top 4 types make up 

#Print Table
count_prop

```


The top 4 common property types are "Entire rental unit","Private room in rental unit","Entire residential home" and "Entire townhouse". The top 4 types make up 60.66%, 11.48%, 6.48%, and 2.66% of the total listings


This will also make it easier for our regressions at a later stage given this is categorical variables.

```{r}
#Simplify the "property_type" 
listings2 <- listings2 %>%
  
  #Create new names called other for properties not in the top four categories
  mutate(prop_type_simplified = case_when(
    
    #Specifying names to be kept
    property_type %in% c("Entire rental unit",
                         "Private room in rental unit", 
                         "Entire residential home",	
                         "Entire townhouse") ~ property_type, 
    
    #Specifying ot leave remaining in other
    TRUE ~ "Other"))

#We check the `prop_type_simplified` was correctly made
listings2 %>%
  
  #Count each category
  count(property_type, prop_type_simplified) %>%
  
  #Arrange by largest category
  arrange(desc(n))    

#Removing the old property type
listings2 <- subset(listings2, select = -property_type)
  
```


Our table comes out as expected and we can see that all smaller property types are in the other category. 

```{r}
#Using above dataset for the confidence interval calculations
formula_ci <- listings2%>% 
  group_by(prop_type_simplified) %>% 
  
  #Calculate weight's summary statistics for people exercising at least 3 times a week 
  
  # calculate mean, SD, count, SE, lower/upper 95% CI
  summarise(
    average_price=mean(price,na.rm=TRUE), #Mean, we choose to ignore any missing values by setting the 'na.rm = TRUE'
            
    sd_price=sd(price,na.rm=TRUE), #Standard Deviation
            
    count= n(), #Observations
           
    t_critical = qt(0.975,count-1), #T-Critical at 95% Confidence Interval and these observations
            
    se_price=sd_price/sqrt(count), #Standard Error 
           
    margin_of_error= t_critical*se_price, #Margin of Error
            
    price_low= average_price - margin_of_error, #Lower interval
            
    price_high= average_price + margin_of_error) #Upper Interval 

formula_ci

ggplot(formula_ci, aes(x=average_price, y=prop_type_simplified, color=prop_type_simplified)) +

#geom_errorbar function allows us to show the two bars with confidence intervals

geom_errorbar(aes(xmin=price_low, xmax=price_high),width = 0.1, size=0.5)+ 
  
geom_point(aes(x=average_price),size=1)+

  
theme_bw() +
  
theme(legend.position = "none",axis.title.y=element_blank())+
  
  labs(title = "Confidence interval for average price per property type",
       subtitle = "95% confidence intervals overlap",
       x = "Average Price"
       ) +
  NULL
```
The property type seems to have a significant effect on prices. The length of the intervals mainly vary due to the differences in sample size. The most common property type (Entire rental unit) has a small interval because it has the larger sample. We can estimate quite aaccuratly the average price in this category.

### Neighbourhood

Next, we look at the variable `neighbourhood_cleansed`. We use the `count` function to determine how many categories there are and their frequency. 
The top 5 common neighbourhoods are "De Baarsjes - Oud-West","De Pijp - Rivierenbuurt","Centrum-West", "Centrum-Oost" and "WesterPark". The top 5 types make up 16.8%, 12.3%, 10.8%, 8.51%%, and 7.48% of the total listings

```{r}
#Determine how many categories there are and their frequency
count_prop <- listings2 %>% 
  
  #Selecting variable of interest
  select(neighbourhood_cleansed) %>% 
  
  #Counting observations 
  count(neighbourhood_cleansed) %>% 
  
  #Arrange by observations
  arrange(desc(n)) %>% 
  
  #In Percentage
  mutate(percentage=n/sum(n)*100) #Determine the proportion of the total listings the top 4 types make up 

#Print Table
count_prop

```

Looking into this we see that there are many more high observation neighbourhoods compared to property types.

Therefore, we believe it makes more sense to split the neighbourhood by their relative prices. 

We do this below


```{r}
#Setting neighbourhood by price
neighbourhood_group <- listings2 %>% 
  
  #Variable of interest
  group_by(neighbourhood_cleansed) %>% 
  
  #Getting median price
  summarize(price_median = median(price)) %>% 
  
  #Arranging by highest price
  arrange(desc(price_median))

#Print
neighbourhood_group


```

We see that some central neighbourhoods are more expensive, which logically makes sense given this is a large city and that is where tourists and other activities are. 

Let's categorize neighbourhood by price

```{r}
#Simplify the "property_type" 
listings2 <- listings2 %>%
  
  #Adding new variable names
  mutate(neighbourhood_cleansed = case_when(
                                  neighbourhood_cleansed == "Centrum-Oost" ~ "Top 5",
                                  neighbourhood_cleansed == "Centrum-West" ~ "Top 5",
                                  neighbourhood_cleansed == "IJburg - Zeeburgereiland" ~ "Top 5",
                                  neighbourhood_cleansed == "Zuid" ~ "Top 5",
                                  neighbourhood_cleansed == "De Pijp - Rivierenbuurt" ~ "Top 5",
                                  neighbourhood_cleansed == "Oud-Noord" ~ "Top 6-10",
                                  neighbourhood_cleansed == "Watergraafsmeer" ~ "Top 6-10",
                                  neighbourhood_cleansed == "Oud-Oost" ~ "Top 6-10",
                                  neighbourhood_cleansed == "Westerpark" ~ "Top 6-10",
                                  neighbourhood_cleansed == "De Baarsjes - Oud-West" ~ "Top 6-10",
                                  neighbourhood_cleansed == "Noord-West" ~ "Top 11-15",
                                  neighbourhood_cleansed == "Noord-Oost" ~ "Top 11-15",
                                  neighbourhood_cleansed == "Oostelijk Havengebied - Indische Buurt" ~ "Top 11-15",
                                  neighbourhood_cleansed == "Buitenveldert - Zuidas" ~ "Top 11-15",
                                  neighbourhood_cleansed == "Bos en Lommer" ~ "Top 11-15",
                                  neighbourhood_cleansed == "Geuzenveld - Slotermeer" ~ "Remaining",
                                  neighbourhood_cleansed == "Slotervaart" ~ "Remaining",
                                  neighbourhood_cleansed == "De Aker - Nieuw Sloten" ~ "Remaining",
                                  neighbourhood_cleansed == "Osdorp" ~ "Remaining",
                                  neighbourhood_cleansed == "Gaasperdam - Driemond" ~ "Remaining",
                                  neighbourhood_cleansed == "Bijlmer-Centrum" ~ "Remaining",
                                  neighbourhood_cleansed == "Bijlmer-Oost" ~ "Remaining"))
                                  
                                
#Check the `prop_type_simplified` was correctly made
listings2 %>%
  
  #Counting by number of observations
  count(neighbourhood_cleansed) %>%
  
  #Displaying in descending order
  arrange(desc(n))    

```


### Minimum nights

Let's first look into how minimum nights look at Airbnb Amsterdam. 

```{r}
#Find out the most common values for the variable `minimum_nights`
listings2 %>%
  
  #Count Observations
  count(minimum_nights) %>%
  
  #Arrange by observations
  arrange(desc(n))

```


By looking into the vairable `minimum_nights`, we found out that airbnb most commonly required people to stay for at least 2 nights. The majority of users tend to spend less than a week, which indicates that Airbnb is most commonly used for travel purposes, i.e., as an alternative to traditional hotels.. 

There are also some variables that stand out i.e. minimum nights of 1,100 days (3 years minimum rent). These individuals are probably looking for long term renters.

We only want to include listings in our regression analysis that are intended for travel purposes, i.e. no more than 4 days.

```{r}
#Filter the Airbnb data so that it only includes observations with `minimum_nights <= 4`
listings2 <- listings2 %>% 
  filter(minimum_nights <= 4)

```


### Dropping NA's 

We then skim the dataset to see if further data wrangling is required.

```{r}
skim(listings2)
```

As we can see, review_scores_rating, reviews_per_month, host_is_superhost, bedrooms and beds still have missing values. We will drop unreviewed units for now and as these units will likely be less accurate in terms of price / review ratings. Similarly for bedrooms and beds, we drop missing values.

```{r}
#Dropping values

listings2 <-  listings2 %>% 
  
  #Choosing which variables to drop NAs from
  drop_na(bedrooms,beds,host_is_superhost,review_scores_rating,reviews_per_month)

#Skimming to confirm code works as intended. 
skim(listings2)
```

### Dropping Rating 0 

We also know that ratings on Airbnb are 1-5, therefore there must be an issue with reviews that are 0 out of 5. 

Let's remove these from our data

```{r}

#Dropping reviews at 0
listings2 <- listings2 %>% 
  filter(review_scores_rating > 0)

```


### Final skim of data

Let's take a final skim of the data

```{r}
skim(listings2)
```



We now have wrangled our data sufficiently and have:
- 4 character variables ready for analysis with not too many categories.
- 2 Date variables with no missing values
- 2 Logical variables with no missing variables
- 9 range of numeric variables with no missing values. 


We also have 11.4 thousand observations. 

We will now explore how these variables affect price.

## Visualisations
By visualising the relationship between price and the variables that we believe will affect the price substantially, we hope to identify a noticeable correlation between price and each of those variables and use statistical modelling to further investigate their relationships and provide possible explanation.

### Overview of Price
We first take a look at the price. 

```{r}
#Overview of price
favstats(listings2$price)
```

We see that price ranges from 4 to 8,000 per night with a mean of 154 and median of 130 (i.e. some left skew)

We create the density plot of price.

```{r}

#Create a density plot of prices
ggplot(listings2,aes(x=price))+
  
  #Using a density plot
  geom_density()+
  
  #Adding useful titles
  labs(title="Density plot of listing Airbnb prices",
       x="Price",
       y="Density") + 
  
  #Minimal theme
  theme_minimal()



#Create a density plot of log of prices
ggplot(listings2,aes(x=log(price)))+
  
  #Density plot
  geom_density()+
  
  #Useful Labes
  labs(title="Density plot of listing Airbnb (log) prices",
       x="Log Price",
       y="Density") + 
  
  #Minimal Theme
  theme_minimal()
```

From here forward we will use Log which is more normally distributed. We can see that there are some peaks and lows on the graph which we connect to well-known disposition of people to round numbers, i.e. setting price to be USD 140 instead of USD 137 or  USD 142. We assume that the graph would be smooth and almost perfectly normally distributed without this feature




### Location/ Neighbourhood

First, we skimmed the neighbourhood_cleansed data to analyse the distribution of price of listings depends on neighbourhood. 
From the table below,  we found out that median price will better suits the purpose of our research than the mean price because the distribution of price of each neighbourhood is greaatly skewed with extreme outliers. For example all neighbourhoods have lower median than mean price while the most expensive property costs USD8,000, causing a large standard deviation. Hence, standard deviation is unusually large among neighbourhood.

```{r}
#Analyse the distribution of price of listings depends on neighbourhood
favstats(price~neighbourhood_cleansed,data=listings2) %>% 
  
  #Arrange by count
  arrange(desc(n)) 

```

We then plot a density graph to see the price distribution of the most popular neighbourhood.

```{r}


#Create the dataset of the top neighbourhood and the price
listings_neigh<-listings2 %>% 
  
  #Group by variable we are looking at
  group_by(neighbourhood_cleansed) %>% 
  
  #ANd get the price
  summarize(price=price)

listings_neigh$new <- factor(listings_neigh$neighbourhood_cleansed, levels = c("Top 5", "Top 6-10", "Top 11-15", "Remaining"))

#Plot the density graph
ggplot(listings_neigh,aes(x=log(price), y = desc(new), fill = new))+
  
  #Density Ridges Plit
  geom_density_ridges(alpha=0.3) +    
  
  #Useful lables
  labs(      
      title = "Difference in price by region expensiveness",
      subtitle="Density plot for prices in different region groups",
      x = "Price per night (log)",
      y = "Density") + 
      theme_classic() + 
  
  #removing y-axis 
    theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  
  #Title of Legend
  guides(fill=guide_legend(title="Neighbourhood regions"))+ 
  
  #Plotting a vertical line at the median
  geom_vline(xintercept = median(log(listings2$price)), colour = "#001e62")+
  NULL


```

The graph shows that the neighbourhoods vary in price and will likely be a good predictor for our analysis later on. 

Let's look at the median price by neighbourhood as well: 


```{r}
#Calculate the median price of different neighborhood
median_per_neighborhood <- listings2 %>% 
  
  #Grouping by variable
  group_by(neighbourhood_cleansed) %>% 
  
  #We want median price
  summarise(median_price = median(price))

#Plot the graph
ggplot(median_per_neighborhood,
       
       #Price versus neighbourhood
       aes(x = reorder(neighbourhood_cleansed, median_price),
           y= median_price)) +
  
  #Columns chart
  geom_col(fill = "skyblue") +
  
  #USeful labes
  labs(
    title = "Median price per night per Neighborhood",
    x="Neighborhood",
    y="Median Price"
    ) +
  
  #To flip axis
  coord_flip() +
  
  #Simple theme
  theme_bw() +
  NULL

```

Plotting on a median price basis indicates that these prices are still indeed impacted by how close they are to center.



### Number of Bedrooms
We skimmed our data to summarise the price distribution based on number of bedrooms. 

From the table below, we noticed that listings with more than five bedrooms have less than 10 samples, therefore, we decided to only include properties with up to five bedrooms. Furthermore, we found out that median price will better suit the purpose of our research than the mean price because the distribution of price based on number of bedrooms is greatly skewed due to extreme outliers. Therefore, we believe that the median price gives better understanding of the relationship between the price and the number of bedrooms

```{r}
#Analyse the distribution of price of listings depends on number of bedrooms
favstats(price~bedrooms, data=listings2)

```
The graph below shows that the listings having more bedrooms have a higher median price.

We would like to plot this information

```{r}
#Filter the bedrooms under 5 to remove outliers
listings2 <- listings2 %>% 
  filter(bedrooms<=5)

#Median calculations
median_per_bedroom <- listings2 %>% 
  
  #By Bedroom
  group_by(bedrooms) %>% 
  
  #Summarized by median price
  summarise(median_price = median(price))

#Plotting the graph
ggplot(median_per_bedroom,
       
       #Bedroom by price
       aes(x = reorder(bedrooms,median_price),
           
           #Price on Y Axis
           y= median_price)) +
  
  #in Column format
  geom_col(fill = "orchid3") +
  
  #With useful labelss
  labs(
    title = "Median price per night per bedrooms",
    x="Number of Bedrooms",
    y="Median Price"
    ) +
  
  #To flip axis
  coord_flip() +
  
  #Simple theme
  theme_bw() +
  NULL
```

We see a strong relationship with number of bedrooms and price.

We assume number of bedrooms will have high correlation with accommodation and number of beds and will therefore leave those two variables out for now. 


### Ratings 
We skimmed our data to summarise the price distribution based on the rating score.

```{r}
#Analyse the distribution of price of listings depends on the rating score
favstats(price~review_scores_rating,data=listings2)
```



By drawing a regression line between the median price and the ratings, we concluded that they share a positive correlation, which means higher ratings have higher median price, and vice versa.

We will use two different methods for this, first we will use the median for each rating creating a smaller subset of datapoints:

```{r}
##Create the data of price and score rating
median_per_rating <- listings2 %>% 
  
  #Group by review
  group_by(review_scores_rating) %>% 
  
  #Summarize by median price
  summarise(median_price = median(price)) %>% 
  
  #Exclude NA's 
  na.omit()


#Plotting
ggplot(median_per_rating,
       
       #Review scores vs median price
       aes(x = review_scores_rating,
           y= median_price)) +
  
  #Coloring red dots
  geom_point(color="red") +
  
  #Adding useful titles
  labs(title = "Median price per night vs. Ratings",
    x="Ratings",
    y="Median Price"
    ) +
  
  #Adding a trend line
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Simple theme
  theme_bw() +
  
  ylim(0, 200) + 
  NULL


```


We see some relationship between price and ratings. Let's explore this further and see if this depends on the room type.  

```{r}
#Plotting by rating but log of price
ggplot(listings2, aes(x = review_scores_rating, y = log(price), color = room_type)) + 
  
  #In red color 
  geom_point(alpha = 0.5) + 
  
  #And adding a trendline
  geom_smooth(se = F, method = "lm", color = "black") + 
  
  #In minimal Theme
  theme_bw() + 
  
    #Adding useful titles
  labs(title = "Log price per night vs. Ratings",
    x="Ratings",
    y="Log Price"
    ) +
  
  facet_wrap(~ room_type, scales = "free") + 
  
  guides(color=F) + 
  
  NULL
```

Interestingly, especially hotel rooms are sensitive to review ratings. 

### Superhosts

Let's first look at a key summary

```{r}
#Analyse the distribution of price of listings depends on the rating score
favstats(price~host_is_superhost,data=listings2)
```

Interestingly, non-superhosts seem to have a higher price than superhosts. Let's plot some relationships to explore this further.

```{r}
#Create the data of price, score rating, and superhost
median_per_rating1 <- listings2 %>% 
  
  #grouping by review score
  group_by(review_scores_rating) %>% 
  
  #Summarizing by price and superhost
  summarise(median_price = median(price),
            host_is_superhost=host_is_superhost) %>% 
  
  #Excluding NA's
  na.omit()

#Plotting the dataset 
ggplot(median_per_rating1,
       
       #By same as above but including host is superhost
       aes(x = review_scores_rating,
           y= median_price, 
           colour = host_is_superhost)) +
  
  #Adding scatterplot
  geom_point() +
  
  #Adding useful labels
  labs(title = "Median price per night vs. Ratings",
    x="Ratings",
    y="Median Price"
    ) +
  
  #Adding Trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Adding a simple theme
  theme_bw() +
  
  #Adding a legend
  guides(color=guide_legend(title="Host is Superhost"))+
  
  #Wrapping by host type to get two different charts
  facet_wrap(~host_is_superhost) +
  
  NULL

```

Although both mean and median price for listings by non-superhost were higher than that by superhost, the regression analysis above shows that the correlation between ratings and median prices is higher for superhost. Therefore, the median price of listings by superhost is more affected by the change in ratings than that by non-superhost.  

Now let's also take a look at the effect from superhosts themselves:

```{r}

#Plotting by host type
ggplot(listings2,
       
       #Adding key variables
       aes(x=host_is_superhost,
           y=log(price), 
           fill = host_is_superhost))+
  
  #Looking at a boxplot for distribution
  geom_boxplot()+
  
  #Adding useful labels
  labs(title = "Superhost versus non superhosts price distributions",
    x="Superhost",
    y=" Log Price"
    )+
  
  #Removing legend
  guides(fill = F) + 
  
  #Simple Theme
  theme_bw() + 
  
  NULL
```
With more extreme outliers, the box plot of non-superhosts shows higher standard deviation  compared to that of superhost.Let's confirm this:

```{r}
#Plot the density graph
ggplot(listings2,
       aes(x=log(price), 
           y = host_is_superhost, 
           fill = host_is_superhost))+
  
  #Density Ridges Plit
  geom_density_ridges(alpha=0.3) +    
  
  #Useful lables
  labs(      
      title = "Prices by host type",
      x = "Price per night (log)",
      y = "Density") + 
      theme_classic() + 
  
  #Title of Legend
  guides(fill=F)+ 
  
  #Plotting a vertical line at the median
  geom_vline(xintercept = median(log(listings2$price)), colour = "#001e62")+
  NULL
```

Based on the graph above, the distribution of superhost seems to have a greater variation. However, the distribution of superhost has a lower standard deviation than that of non-superhost. Therefore, we believe that the graph above is greatly influenced by the number of samples included, i.e. 1,634 superhost vs 9,767 non-superhost.  


### Number of reviews


Similarly we can graph a relationship between number of reviews and price. 

As this is a numerical variable with many ranges we will not use favstats to look into this. 


```{r}
ggplot(listings2, 
       
       #Plotting reviews by price
       aes(x = number_of_reviews,
           y= log(price))) +
  
  #Adding color to the chart
  geom_point(color="red", alpha = 0.3) +
  
  #Adding useful labels
  labs(title = "Price per night vs. number of Reviews",
    x="Number of Reviews",
    y="Log Price"
    ) +
  
  #Adding a trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Adding BW Theme
  theme_bw() +
  
  NULL
```

We see that as the number of reviews increases the price falls.

Let's check if this holds across categorical variables

```{r}
ggplot(listings2, 
       
       #Plotting reviews by price
       aes(x = number_of_reviews,
           y= log(price),
           color = room_type)) +
  
  #Adding color to the chart
  geom_point(alpha = 0.5) +
  
  #Adding useful labels
  labs(title = "Price per night vs. number of Reviews",
    x="Number of Reviews",
    y="Log Price"
    ) +
  
  #Adding a trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Adding BW Theme
  theme_bw() +
  
  #Wrapping by host type to get two different charts
  facet_wrap(~room_type, scales ="free") + 
  
  guides(color = F) + 
  
  NULL
```
This is super interesting to see because we see that the relationship depends on room types. Therefore it is important to control for room type when looking at the effect of number of reviews!


### License 


Let's first look at a summary of the data:


```{r}
#Analyse the distribution of price of listings depends on the rating score
favstats(price~license,data=listings2)
```
We see that the listings with license have higher mean and median prices. 

By graphing a boxplot, we see that properties with license have higher Q1, median and Q3 value than properties without license. Hence, we conclude that properties with licence are more expensive than the others.

```{r}

#Plotting the data
ggplot(listings2,
       aes(x=license,
           y=log(price)))+
  
  #In Wheat Color
  geom_boxplot(fill="wheat2")+
  
  #Useful labels
  labs(title = "Price per night vs. License",
    x="License",
    y=" Price"
    )+
  
  #BW Theme
  theme_bw()+ 
  
  NULL

```
We see that there is a higher spread on prices of properties without licenses and a slightly lower median price. 


### Room type


```{r}
#Analyse the distribution of price of listings depends on the rating score
favstats(price~room_type,data=listings2)
```

There seems to be an extremely strong relationship between room type and price. This is good for our analysis but let's first plot it further.

First let's visualize the median price:

```{r}
#Calculate the median price of different room types
median_per_room <- listings2 %>% 
  
  #By Room
  group_by(room_type) %>% 
  
  #In median Prices
  summarise(median_price = median(price))

#Plot the graph
ggplot(median_per_room,
       
       #Reorder by price
       aes(x = reorder(room_type, median_price),
           
           #Price on Y Axis
           y= median_price)) +
  
  #Column Chart
  geom_col(fill = "skyblue") +
  
  #Useful Labels
  labs(
    title = "Median price by room_type",
    x="Room Type",
    y="Median Price"
    ) +
  
  #Flipping for aesthetics
  coord_flip() +
  
  #Simple theme for aesthetics
  theme_bw() +
  NULL
```
We see that entire homes and hotel rooms are especially expensive. We would like to plot the density of this to explore it further:


```{r}
#Density Plot
ggplot(listings2,
       aes(x=log(price), 
           y = room_type, 
           fill = room_type))+
  
  #Density Ridges Plit
  geom_density_ridges(alpha=0.3) +    
  
  #Useful lables
  labs(      
      title = "Prices by room type",
      x = "Price per night (log)",
      y = "Density") + 
      theme_classic() + 
  
  #Title of Legend
  guides(fill=F)+ 
  
  #Plotting a vertical line at the median
  geom_vline(xintercept = median(log(listings2$price)), colour = "#001e62")+
  NULL

```
Interestingly although entire homes or apartments are the most expensive in terms of median, we see that some hotels are also extremely expensive.

We also see that these distributions are multimodal - i.e. prices are clustered around specific levels. 

```{r}
#Using above dataset for the confidence interval calculations
formula_ci <- listings2%>% 
  group_by(room_type) %>% 
  
  #Calculate weight's summary statistics for people exercising at least 3 times a week 
  
  # calculate mean, SD, count, SE, lower/upper 95% CI
  summarise(
    average_price=mean(price,na.rm=TRUE), #Mean, we choose to ignore any missing values by setting the 'na.rm = TRUE'
            
    sd_price=sd(price,na.rm=TRUE), #Standard Deviation
            
    count= n(), #Observations
           
    t_critical = qt(0.975,count-1), #T-Critical at 95% Confidence Interval and these observations
            
    se_price=sd_price/sqrt(count), #Standard Error 
           
    margin_of_error= t_critical*se_price, #Margin of Error
            
    price_low= average_price - margin_of_error, #Lower interval
            
    price_high= average_price + margin_of_error) #Upper Interval 

formula_ci

ggplot(formula_ci, aes(x=average_price, y=room_type, color=room_type)) +

#geom_errorbar function allows us to show the two bars with confidence intervals

geom_errorbar(aes(xmin=price_low, xmax=price_high),width = 0.1, size=0.5)+ 
  
geom_point(aes(x=average_price),size=1)+

  
theme_bw() +
  
theme(legend.position = "none",axis.title.y=element_blank())+
  
  labs(title = "Confidence interval for average price per room type",
       subtitle = "95% confidence intervals overlap",
       x = "Average Price"
       ) +
  NULL
```
The confidence intervals' lengths are very different between each room type. Shared and hotel rooms have wide widths. There is a big uncertainty related to their average price. On the other side, we can estimate quite accurately the entire and private homes' average.

### Property Type


Let us look into the statistics first:


```{r}
#Analyse the distribution of price of listings depends on the rating score
favstats(price~room_type,data=listings2)
```

There seems to be a very strong relationship between property type and price. Lets plot the medians again:

```{r}
#Calculate the median price of different room types
median_per_prop <- listings2 %>% 
  group_by(prop_type_simplified) %>% 
  summarise(median_price = median(price))

#Plot the graph
ggplot(median_per_prop,
       aes(x = reorder(prop_type_simplified, median_price),
           y= median_price)) +
  
  #Column type
  geom_col(fill = "skyblue") +
  
  #Useful labels
  labs(
    title = "Median price by property type",
    x="Room Type",
    y="Median Price"
    ) +
  
  #Flipping for aesthetics
  coord_flip() +
  
  #Simple theme
  theme_bw() +
  NULL
```

This is very useful but let's also take a look at the distribution: 

```{r}
#Density Plot
ggplot(listings2,
       aes(x=log(price), 
           y = prop_type_simplified, 
           fill = prop_type_simplified))+
  
  #Density Ridges Plit
  geom_density_ridges(alpha=0.3) +    
  
  #Useful lables
  labs(      
      title = "Prices by property type",
      x = "Price per night (log)",
      y = "Density") + 
      theme_classic() + 
  
  #Title of Legend
  guides(fill=F)+ 
  
  #Plotting a vertical line at the median
  geom_vline(xintercept = median(log(listings2$price)), colour = "#001e62")+
  NULL

```
There is a very distinct pattern between property types and this will likely be a useful regressor for our analysis. 

### Avaialability next 30 days

Let's also look at availability next 30 days which we hypothesize will be an indicator of popularity. 

```{r}

#Summarizing median price by availability
listings_availability<-listings2 %>% 
  group_by(availability_30) %>% 
  summarize(price=median(price))

#Plotting scatterplot of availability 
ggplot(listings_availability, 
       aes(x = availability_30,
           y= log(price))) +
  
  #Points in red
  geom_point(color="red") +
  
  #Useful Labels
  labs(title = "Log Price Per Night versus Availability",
    x="Availability next 30 days",
    y="Log Price"
    ) +
  
  #Adding a trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Simplified theme
  theme_bw() +
  NULL
```
The more availability, the higher the price, which indicates that more premium rooms are booked less often or are less often fully booked. 

This goes against our initial thought that less availability would be popular rooms and therefore more expensive! Good that we looked into this. 


### Instant Bookable

Let's also look at whether or not units are instantly bookable

```{r}
#Analyse the distribution of price of listings depends on the rating score
favstats(price~instant_bookable,data=listings2)
```

Instant bookable seems to be slightly higher distributed. Let's take a look at the graph:

```{r}

#Boxplotting instant bookable vs log prices
ggplot(listings2,aes(x=instant_bookable,y=log(price)))+
  
  #Boxplot format
  geom_boxplot(fill="wheat2")+
  
  #Useful labels
  labs(title = "Distribution of prices depending on whether or not units are instantly bookable",
    x="Instantly Bookable",
    y="Log Price"
    )+
  
  #Simople Theme
  theme_bw()

```
There seems to be little to no difference between whether or not the units are bookable, however, we will still look further into this in the regression.


### Host Since


Let's also look at when they have been host since:

```{r}

#Plotting scatterplot of availability 
ggplot(listings2, 
       aes(x = host_since,
           y= log(price))) +
  
  #Points in red
  geom_point(color="red", alpha = 0.2) +
  
  #Useful Labels
  labs(title = "Log price per night versus how long the host has been active on Airbnb",
    x="Host since (date)",
    y="Log Price"
    ) +
  
  #Adding a trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Simplified theme
  theme_bw() +
  NULL
```


There seems to be little to no relationship here and we will likely not need to consider it going forward. 

Let's check across categoris


```{r}

#Plotting scatterplot of availability 
ggplot(listings2, 
       aes(x = host_since,
           y= log(price), 
           color = prop_type_simplified)) +
  
  #Points in red
  geom_point(alpha = 0.5) +
  
  #Useful Labels
  labs(title = "Log price per night versus how long the host has been active on Airbnb",
    x="Host since (date)",
    y="Log Price"
    ) +
  
  #Adding a trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Simplified theme
  theme_bw() +
  
  facet_wrap(~prop_type_simplified, scales = "free") + 
  
  guides(color = F) + 
  
  NULL
```

This seems to hold true across a variety of categories and we will not consider it going forward. 


### Last Review


Let's also look at whether last review date has an impact

```{r}

#Plotting scatterplot of availability 
ggplot(listings2, 
       aes(x = last_review,
           y= log(price))) +
  
  #Points in red
  geom_point(color="red", alpha = 0.2) +
  
  #Useful Labels
  labs(title = "Log price per night versus when the last review was",
    x="Last Review (date)",
    y="Log Price"
    ) +
  
  #Adding a trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  #Simplified theme
  theme_bw() +
  NULL
```

We see a slight relationship between price and the date of last review. We also noticed that some properties do not have a recent review probably due to covid-19 outbreak. 

We will plot the density for reference

```{r}

#Plotting scatterplot of availability 
ggplot(listings2, 
       aes(x = last_review)) + 
  
  geom_density(fill = "blue", alpha = 0.2) + 
  
  #Useful Labels
  labs(title = "Distributions of last reviews",
    x="Last Review (date)",
    ) +

  #Simplified theme
  theme_bw() +
  NULL
```

Although many properties did not receive a review during the Covid-19 outbreak, we will still include these data in our analysis. 

```{r}

#Plotting scatterplot of availability 
ggplot(listings2, 
       aes(x = last_review,
           y= log(price), 
           color = prop_type_simplified)) +
  
  #Points in red
  geom_point(alpha = 0.5) +
  
  #Useful Labels
  labs(title = "Log price per night versus when the last review was",
    x="Last Review (date)",
    y="Log Price"
    ) +
  
  #Adding a trendline
  geom_smooth(method=lm,colour="black",alpha=0)+
  
  facet_wrap(~prop_type_simplified, scales = "free", ncol = 3) + 
  
  #Simplified theme
  theme_bw() +
  
  guides(color =F) + 
  NULL
```
We see that this relationship holds across a variety of properties. 

### Paired relationship overview
We plotted a GG pairs plot to get a comprehensive overview of the relationship between the price of listings and the selected variables. 

We only plot the numerical variables where we can get a correlation and scatterplot of the relationship


```{r}
#Relatonship between the price and variables, starting with numerical variables
listings2 %>% 
  
  #Choosing our variables
  select(price, #Variable we are trying to explain
         accommodates, 
         review_scores_rating, 
         number_of_reviews, 
         minimum_nights, 
         reviews_per_month, 
         bedrooms, 
         beds, 
         availability_30,
         last_review) %>% 
  
  #Size and aesthetics
  ggpairs(aes(alpha=0.2))+
  theme_minimal(base_size=8)

```
From the above we see that for price the most correlated variables is the number of accomodates or bedrooms (although these are  correlated with 0.73 and will likely not both be included). However, from here it seems that perhaps it is better to focus on accommodates rather than bedrooms. 

It is worth noting that some of the less correlated variables seem to be review scores, number of reviews, however, we will still try and test these in our regression. 

Unfortunately, GGPairs does not work well with categorical variables and we will use that data we extracted above as an indicator for whether or not these variables will be useful going forward.

# Acknowledgements

- The data for this project is from [insideairbnb.com](insideairbnb.com)



# Authors

Karim El Asmar, Stepan Emelianenko, Nelly Gray, Ziqi Li, Ray Park, Shirley Wan, Ditlev Meulengracht
